---
title: "Election Data"
author: "Group 32"
date: "5/22/2019"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo=FALSE, message=FALSE)
library(data.table)
library(R.utils)
library(openintro)
library(dplyr)
library(ggplot2)
library(formattable)
library(tidyr)
library(tm)
library(knitr)
library(openintro)

source("~R/a7-rscript.R") 
source("~R/calculation function.R")
source("~R/chart_two.R") 
```

# Summary 

Using information about the US Presidential elections found in the presidential_2008-2016 
csv file, we sought to find out some details regarding the political parties and votes. 
First, we wanted simple answers such as the total percentage of democratic voters in the 
2008 election, the total vote data of the state of Alaska (since it is missing from the 
csv file data), and which state had the maximum democratic votes in 2008. Next, we wanted 
to find out if there was a correlation between median income and Republican votes and 
whether that correlation was positive or negative. Finally, we wanted to see a geographic 
visual of all counties in the country and which political party dominated, Democrat or 
Republican.


# Simple Answers

```{r}
dem_votes <- percent_votes("dem", "2008", table)
```

The total percentage of democratic votes in the 2008 election was **`r dem_votes`** 

This is the total vote data for our state of Washington:
```{r}
state_list <- state_info("WA")
kable(state_list)
```

```{r}
compare <- compare_votes("dem", "2008", "max")
compare_state <- abbr2state(compare) 
```
The state that had the maximum democratic votes in 2008 was **`r compare_state`**.

# Correlation
```{r}

correlation_function(2008)

```

In this scatterplot, we see information regarding the 2008 US Presidential Election.
Here, we tried to find a correlation between the median income of voters and the 
number of Republican votes. Using a line of best fit, we discovered that there is a 
positive correlation between these two variables. We expect that as median income 
increases, the number of Republican votes increase.



# Majority
```{r}

majority_func(2008)

```

Here, we see some information about the 2008 US Presidential Election. In this map,
the red highlights all counties in which the Democratic party was the most popular
vote. Also, the blue highlights all counties where the Republican party was the most
popular. According to this map diagram, Republican votes dominate the country 
geographically.
